This chapter serves as an overview of select existing online reservation systems and can be taken as a form of market research for the booking system to be created.

The overview is meant to be qualitative rather than quantitative, focusing on the exploration of features provided by a select few systems and the user experience while using those systems. The systems chosen for the overview are Acuity Scheduling\footnote{Acuity Scheduling (\url
{https://www.acuityscheduling.com})}, Reservio\footnote{Reservio (\url
{https://www.reservio.com})}, Square Appointments\footnote{Square Appointments (\url
{https://squareup.com/us/en/appointments})}, and Wix\footnote{Wix (\url
{https://www.wix.com})}.

The criteria used to choose the systems for the overview are the following:
\begin{itemize}
    \item \textbf{Popularity} --- The system must be popular with the public. Without an extensive quantitative survey, this is a difficult criterion to evaluate. As a rough estimate, the system's ranking in the Google search results for the queries \enquote{online reservation system,} \enquote{online booking system,} and \enquote{online scheduling system} was used. If the systems appeared on the first couple of pages of the results, they were considered popular enough. Some flaws of this approach are, for instance, results personalization based on geographic location, as well as search engine optimization (SEO) techniques used by the systems. Similarly, different systems could have been discovered by using other search queries and search engines. However, despite the flaws of this approach, it still seemed to yield good enough results.
    \item \textbf{Localization} --- The system must have English localization.
    \item \textbf{Price} --- The system must offer a free version of its service (at least as a limited-time trial). Additionally, it must not require payment information to sign up for the free version.
\end{itemize}

\section{Acuity Scheduling}
\label{part:acuity_scheduling}

\input{content/existing_reservation_systems/acuity_scheduling}

\section{Reservio}
\label{part:reservio}

\input{content/existing_reservation_systems/reservio}

\section{Square Appointments}
\label{part:square_appointments}

\input{content/existing_reservation_systems/square_appointments}

\section{Wix}
\label{part:wix}

\input{content/existing_reservation_systems/wix}

\section{Summary}
\label{part:existing_reservation_systems_summary}

\input{content/existing_reservation_systems/summary}
