This chapter describes the prototype implementation of the designed system, as well as its testing and evaluation.

For the entire implementation, TypeScript, Node.js, and npm were used. The reason behind this choice is both prior experience with this ecosystem of the author of this thesis, as well as its popularity for full-stack web development, ensuring high amount of useful supporting resources.

TypeScript~\cite{typescript} is a popular \enquote{strongly typed programming language that builds on JavaScript.} It \enquote{adds additional syntax to JavaScript to support a tighter integration with (...) an editor} to \enquote{catch errors early.} The code \enquote{converts to JavaScript, which runs anywhere JavaScript runs: in a browser, on Node.js, Deno, Bun.} TypeScript is a static type checker, meaning that it performs type checking only at compile time, not during the runtime.

\begin{sloppypar}
Node.js~\cite{node_js} is a \enquote{cross-platform JavaScript runtime environment that lets developers create servers, web apps, command line tools and scripts.} It is \enquote{built on the V8 JavaScript engine} (which is also used~\cite{v8} by Chromium-based web browsers, such as Google Chrome). The Node.js documentation~\cite{node_js} further states that \enquote{npm is the standard package manager for Node.js,} with npm~\cite{npm} claiming that it is \enquote{the largest software registry in the world.}
\end{sloppypar}

Each application that is part of the implementation is kept in a separate directory: \textit{booking-service} for the booking service, \textit{booking-api-gateway} for the API gateway, and \textit{booking-client-app} for the client application. These directories with the source code are included in the content of the digital attachment~\ref{part:contents_of_the_digital_attachment}.

\begin{sloppypar}
Every application directory contains a \textit{package.json} file and an \textit{npm-shrinkwrap.json} file. These files in the JavaScript Object Notation (JSON) data format are both related to npm, with \textit{package.json}~\cite{npm_docs} describing many things, including general metadata about the project (package name, version adhering to semantic versioning, license information, author information, important URLs, etc.), npm scripts' definitions, lists of npm dependencies (of various types) along with their version, application entrypoints, and information about supported environments. The file \textit{npm-shrinkwrap.json} is then generated by npm when installing dependencies (using the \mintinline{sh}{npm install} command) and it is a publishable variant of the \textit{package-lock.json} file used by default to describe \enquote{the exact (dependency) tree that was generated, such that subsequent installs are able to generate identical trees, regardless of intermediate dependency updates.} This ensures consistently reproducible dependency installations. Dependencies are installed into the \textit{node\_modules} directory of each project (this directory is not included in the source code).
\end{sloppypar}

To fulfill non-functional requirement~\ref{req:open_source}, each application directory also contains a \textit{LICENSE.txt} file with the popular permissive open-source MIT license (which is also correctly denoted in the \textit{package.json} files) and each application only uses dependencies with compatible permissive open-source licenses.

Furthermore, the file \textit{Containerfile} is included in each application directory. \textit{Containerfile}~\cite{podman_github} (which is an alternative name for \textit{Dockerfile}) is \enquote{a configuration file that automates the steps of creating a container image.} Application container images can then be created using tools like Docker, Podman, and Buildah, either in the Docker image format or in the Open Container Initiative (OCI) image format (which is largely similar). These container images can then used by orchestration tools (such as Kubernetes) for~\cite{kubernetes} \enquote{automating deployment, scaling, and management of (...) applications}. Additionally, the \textit{compose.prod.yaml} Compose file is attached to enable easily building and running all the service containers in production mode using tools like Docker Compose, and the \textit{booking-service} directory contains a \textit{compose.yaml} file with the dependant services for the booking service to run (and thus is useful for development). This fulfills non-functional requirement~\ref{req:cloud_native}.

Lastly, each application directory contains a \textit{README.md} file in the Markdown format, describing how to run it, and a \textit{.env.template} file with a template for the environment variables that need to be set for the application to run.

\section{Booking Service}
\label{part:i_booking_service}

\input{content/implementation/booking_service}

\section{API Gateway}
\label{part:i_api_gateway}

\input{content/implementation/api_gateway}

\section{Client Application}
\label{part:i_client_application}

\input{content/implementation/client_application}

\section{Testing and Evaluation}
\label{part:testing_and_evaluation}

\input{content/implementation/testing_and_evaluation}
