To summarize this overview, among the four online reservation systems included in the overview -- Acuity Scheduling, Reservio, Square Appointments, and Wix -- there were many similarities and common features.

One of the similarities was the overall process of setting up a business account, filling out basic information about the business and setting up certain services, classes, or events for the clients to book. After this, the system would let the users create a booking website under the subdomain of the service or under a custom domain (which was always a premium feature). Customers could then access the website, view the information about the business, the services or events provided, and create a booking.

All systems also featured some options to accept payments, in addition to sending out emails with booking details and reminders. There was always some possibility to embed components or iframes with booking functionality to other websites, and an API for developers to integrate the system with other software (the API was always platform specific though). Calendar synchronization and multi-user accounts (with adjustable permissions) were also common features.

The main differences (excluding pricing strategies and the UI) seemed to be the ability to add forms for users to fill out during booking (present in Acuity Scheduling and in Wix's solutions), the ability to create a custom venue map with seating and areas sold under different ticket types (present in Wix Events).

Those platforms that focus on building websites (Wix and -- the owner of Acuity Scheduling -- Squarespace) offer more features for extensive booking website customization. On the other hand, Square Appointments from Square who focuses on financial services, offers the most features for payment processing, customer subscriptions, and financial reporting. Finally, Reservio seemed to offer subjectively the simplest business account setup and UI.
