The functional requirements for the system are the following:
\begin{enumerate}[label=\textbf{F\arabic*}, ref=\labelenumi]
    \item \label{req:user_account} \textbf{User account} --- A user without an account must sign up for one to use the system. A user with a user account must be uniquely identified in the system. A user can log into their account and log out of their account.
    \item \label{req:inventory} \textbf{Inventory} --- A user can create an inventory of items for users to book. An inventory can have some basic information attached (such as a name, a description, and contact information). Items can also have information attached, and can be booked by multiple users up to a given maximum capacity.
    \item \label{req:booking} \textbf{Booking} --- A user can view an inventory including its items of a user with a created inventory. A user can book an item from an inventory. A user can view their existing bookings.
    \item \label{req:forms} \textbf{Forms} --- A user with an inventory can attach a form to the inventory. A user who wants to book an item from an inventory with a form must fill out the form.
    \item \label{req:deadlines} \textbf{Deadlines} --- A user with an inventory can limit until when an existing booking of an inventory item can be booked.
    \item \label{req:permissions} \textbf{Permissions} --- A user with an inventory can limit who can book items from their inventory by creating either an allowlist or a denylist of users.
    \renewcommand{\labelenumi}{\textbf{F\arabic{enumi}}*}
    \item \label{req:cancellation} \textbf{Booking cancellation} --- A user can cancel their existing booking. A user with an inventory can cancel an existing booking of item from their inventory as well.
    \item \label{req:edits} \textbf{Booking edits} --- A user can edit their existing bookings' form data.
    \item \label{req:ownership_verification} \textbf{Booking ownership verification} --- A user can easily verify in person that another user is the owner of a booking (for instance by scanning a QR code).
    \item \label{req:rt_updates} \textbf{Real-time item availability updates} --- A user can see real-time availability updates of a user with an inventory of items.
    \item \label{req:filtering} \textbf{Inventory filtering} --- A user can request a user's inventory of items filtered by item attributes.
    \item \label{req:custom_domain} \textbf{Custom domain} --- A user can use a custom domain for their identification in the system without setting up their own server.
    \item \label{req:data_exim} \textbf{Data export and import} --- A user can export and import their data in an open, standardized, machine-readable data format.
    \item \label{req:directory} \textbf{Inventory directory} --- A user with an inventory set up can opt in to have their inventory listed in a publicly accessible directory of user inventories. A user can access the directory of user inventories and filter/sort it by inventory attributes, or search it using natural language queries.
    \item \label{req:calendar_sync} \textbf{Calendar synchronization} --- A user can have their bookings with date and time attributes synchronized with their personal calendar. A user with an inventory set up can have their inventory items with date and time attributes synchronized with their business calendar.
    \item \label{req:notifications} \textbf{Notifications} --- A user can receive email (and possibly other types, such as SMS) notifications about their bookings and inventory items.
    \item \label{req:waitlist} \textbf{Waiting list} --- A user can enter a waiting list for an item that is fully booked. When a booking of that item is cancelled, or the user who the item's inventory belongs to increases the capacity, the item is automatically booked for the first users on the waiting list up to the newly available capacity.
    \item \label{req:payments} \textbf{Payments} --- A user with an inventory can require payments before or after a booking is made. A user can make a payment for a booking they made or are about to make, if that booking requires it.
    \item \label{req:multiuser_account} \textbf{Multi-user account} --- A user account can be used by multiple users. The user that first creates a user account can manage who else can use the account, and can limit their permissions.
    \item \label{req:internationalization} \textbf{Internationalization} --- A user can choose the locale (language, currencies, date and time formats, etc.) they want to use of the system under. A user with an inventory can set up their inventory with multiple different locales.
    \item \label{req:contacts} \textbf{Contacts} --- A user can add users with inventories to their contacts list. A user can view their contacts list and use it to quickly access the inventories of their contacts, as well as view the bookings made for the items of each individual contact.
    \item \label{req:autofill} \textbf{Autofill} --- A user can have their personal information automatically filled into forms during booking. This personal information can be manually entered by the user into a settings section, or automatically saved from previously filled-in forms.
    \item \label{req:automatic_reservations} \textbf{Automatic reservations} --- A user can instruct the system to automatically book selected items from selected inventories for them. Such instructions can for example be to book any appointment-type item at the beginning of every month from a given inventory, and that the event item must occur within a given time range.
\end{enumerate}

This list also includes some requirements that are out of scope for the initial version of the system, but are included for the sake of completeness. These requirements will not be further designed or implemented, but may have some impact for instance on the design of the system, the choice of technologies used, or certain implementation details. Such requirements are marked with an asterisk (\mintinline{text}{*}). Additionally, the item~\ref{req:permissions} will be only only designed, not implemented, to keep the scope of the project to a reasonable degree.

Most of the functional requirements stem from features already present some or all in the reservation systems previously explored. Optional requirement~\ref{req:automatic_reservations} is an original idea, that would could make use of the strengths of the newly designed system.
